Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-02 snapshot_system/failover.tex

Figure~\ref{fig-vo-links} shows the average number of VMs shared by 
a block in the global index as more VMs are added in VO. 
The first 15 VMs are all windows machines, so that explains the initial 
higher values, but for the most part the average number of 
links is between 1.5 and 2.

@@

in our current testbed we have measured the average number of links
per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{vo-fsb-links})
in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
was 11 using a 5\% CDS. From Figure~\ref{vo-fsb-links} you can see that as you add VMs, the average
number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
should continue to increase at a slower rate. 
For the VC model, we have to consider both CDS chunks and 
Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
higher rate. This gives a strong advantage to VC, in that for a large percent of the data (95-99\%), there
is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
}

The figure shows that even as the number of VMs sharing a CDS file block 
increase by 100 times, the availability only decreases
slightly.
The key factor placed is that  $N_1 +N_2 << N_o$, caused by the fact that
the VM-centric approach localizes deduplication and
packs  data blocks for one VM as much as possible.
The extra replicaton for CDS blocks 
also signficantly increses the snapshot availability even a CDS file block
is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig-cds-replication}
shows the advantages of increasing the replication factor for CDS blocks. These figures together show
the advantages of the VM-centric model, and the advantages that separating the replication factor for popular blocks
can have on reliability.

>>>>

Figure~\ref{fig-vo-links} shows the average number of VMs sharing a block in
the global index as more VMs are added in VO.  The first 15 VMs are all windows
machines, so that explains the initial higher values, but for the most part the
average number of links is between 1.5 and 2. Figure~\ref{fig-vo-fsb-links}
shows the average number of VMs sharing a filesystem block (FSB) in the global
index, but only for the 15 windows machines (the last machine has a much larger
hard-drive, and therefore more unique data, which explains the drop-off in the
last datapoint).  This is a reasonable assumption, that a cluster will have one
OS dominating, and for our small dataset the number of links to an FSB
increases as more VMs of the same OS are added. You can see in the plot however
that even though a FSB contains 16K chunks, the average number of links to an
FSB is only several times the number of average links to a chunk. This is
because even in the VO global deduplication model, as long as writes are
batched a single FSB will tend to contain chunks from only a small number of
VMs. Below we show the significant impact the number of links has on VM backup
reliability.

@@

in our current testbed we have measured the average number of links
per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{fig-vo-fsb-links})
in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
was 11 using a 5\% CDS. From Figure~\ref{fig-vo-fsb-links} you can see that as you add VMs, the average
number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
should continue to increase at a slower rate. 
For the VC model, we have to consider both CDS chunks and 
Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
higher rate. This gives a strong advantage to VC, in that for a large percent of the data (95-99\%), there
is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
}

Figure~\ref{fig-vm-availability} shows the reliability of VM backups as storage
nodes fail for different numbers of links to average blocks in the index. We
chose 5 and 11 for the VO and VC block links counts because those are what we
measured in our dataset, and chose higher numbers to account for much larger
datasets. As you can see from the graph, even small changes in the number of
links to VO blocks has a significant impact on reliability, while even a 100
times increase in the VC block link counts only slightly affects VC
reliability.  The key factor placed is that  $N_1 +N_2 << N_o$, caused by the
fact that the VM-centric approach localizes deduplication and packs  data
blocks for one VM as much as possible.  The extra replicaton for CDS blocks
also signficantly increaes the snapshot availability even when a CDS file block
is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig-cds-replication}
shows the advantages of increasing the replication factor for CDS blocks. the
numbers in the graph are only meant to be relative, as we assume higher CDS
block links than we have measured in our dataset (to account for a much larger
body of data). It is easy to see though that increasing the replication of just
the CDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.
